%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Dyllon}{Gagnier}{ % Your name

\href{mailto:dyllongagnier@gmail.com}{dyllongagnier@gmail.com} | 801.725.9919 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.35\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{University of Utah}

\descript{BS/MS Computer Science - Data Management and Analysis}
Dean's List (All Semesters) \\
\location{Grad. May 2019 | Salt Lake City, UT}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Layton High School}

\location{Grad. May 2012 | Layton, UT}

\sectionspace % Some whitespace after the section



%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}


\subsection{Undergraduate}

Data Structures and Algorithms \\
Probability and Statistics \\
Fundamentals of Digital System Design \\
Discrete Mathematics \\
Software Practice \\

\subsection{Graduate}

Computer Networking \\
Databases \\
Machine Learning \\
Natural Language Processing \\
Data Visualization \\
Parallel Programming (GPU) \\
Computational Topology \\


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Languages / Frameworks}
\begin{tightitemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\item Python
\item Java and Spring
\item JavaScript and Typescript
\item C++
\item SQL
\item C\#
\item Racket
\item Haskell
\end{tightitemize}

\subsection{Programming Skills}
\begin{tightitemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\item Software Model Checking
\item Property Based Testing
\item Database Schema Design and Normalization
\item Test Driven Development
\item Automated UI Testing
\item Functional Programming
\item Web Frontend and Backend
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}

LinkedIn:// \href{http://www.linkedin.com/pub/dyllon-gagnier/2a/6b3/808/}{\bf pub/dyllon-gagnier} \\
GitHub:// \href{https://github.com/}{\bf slaymaker1907} \\

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.64\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Goldman Sachs Intern}
\descript{| Private Wealth Management Software Engineer}
\location{ July 2019 - present | Salt Lake City, UT}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\begin{tightitemize}
	\item Developed highly scalable and highly available backend systems supporting asset transfer.
	\item Used Sybase, MongoDB, and a number of rest services to migrate data from a legacy system to a new system while ensuring no data loss in the mapping.
	\item Introduced team to property based testing helping greatly reduce the burden of unit testing while increasing their quality.
\end{tightitemize}

\runsubsection{Goldman Sachs Intern}
\descript{| Private Wealth Management Technology Intern}
\location{ June 2016 -  | Aug. 2018 Salt Lake City, UT}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\begin{tightitemize}
\item Improved existing internal framework by removing database deadlock condition.
\item Developed REST backend for document metadata repository using Java Dropwizard.
\end{tightitemize}

%------------------------------------------------

\runsubsection{University of Utah School of Computing}
\descript{| Teaching Assistant}
\location{ Jan. 2016 - May 2016 | Salt Lake City, UT}
\begin{tightitemize}
\item Taught small to medium sized groups of students about assembly programming and computer architecture.
\item Designed automated test framework for the MARS MIPS assembly simulation program to grade student work quickly and fairly.
\end{tightitemize}

%------------------------------------------------

\runsubsection{Panasonic R\&D Company of America}
\descript{| Software QA Intern}
\location{June 2015 - Aug. 2015 | Salt Lake City, UT}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\begin{tightitemize}
\item Developed complex integration tests for the OpenDOF distributed object framework in C\#, C, and Java. (OpenDOF.org)
\item Performed full QA and testing of the OpenDOF Interface Repository 1.0 (https://interface.opendof.org/)
\end{tightitemize}

\sectionspace

%------------------------------------------------

\runsubsection{General Atomics Aeronautical Systems, Inc.}
\descript{|Software Development Intern}

\location{Dec. 2014 - May 2015 | Layton, UT}
\begin{tightitemize}
\item Wrote automated UI tests for Claw (GUI for image processing on drone images).
\item Developed a module that was able to detect from two images of text with differing texts if one was bolded.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Extracurricular
%------------------------------------------------

%------------------------------------------------
% Special Projects
%------------------------------------------------

\section{Special Projects}
\vspace{\topsep} % Hacky fix for awkward extra vertical space.
\begin{tightitemize}
\item Highly optimized shuffle in CUDA and Rust (see \url{https://github.com/slaymaker1907/quick-shuffle})
\item General purpose IDE for graph based programming (see \url{https://github.com/2graphic/sinap-ide})
\item Wrote a stateless password manager (see \url{https://slaymaker1907.github.io/password/})
\item Wrote a music analysis tool using computational topology to find patterns (see \url{https://github.com/slaymaker1907/baeuler})
\end{tightitemize}
\sectionspace % Some whitespace after the section



\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
